---
title: "Search Ads Performance Report"
author: "KT"
date: "Generated: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  slidy_presentation: 
  html_document: 
editor_options: 
  chunk_output_type: console
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
#manually inputed values
#File Location
filename <- 'C:/Users/kevin/Desktop/Abide/searchAds.json'
#Analysis starting date
start_date <- '2018-09-01'
#Analysis ending date
end_date <- '2018-09-30'
#Number of campaigns to display in output, too many displayed will make the chart difficult to read
num_top_campaigns <- 15
#Number of keywords to display in output
num_top_keywords <- 25
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#notes 
#2.0 Changes
#1)  Included devices data (users that download but did not create an account)
#2)  Make charts more interactive
#3)  Right justify the % column
#4)  Add a check that ensures subscribe date is after click date
#5)  Minor bug/data descrepency fixes 

#low conversion

#Hypothesis for dropoff
#Null: only 36% conversion from downloads to account
#- download to account ratio follows in line with account to subscribe ratio

#Add devices data

#Further analysis: conversions of downloads from devices to accounts to subs with and without ads

#Avg. Time from signup to conversion
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#library loads
library(data.table)
library(readr)
library(dplyr)
library(VIF)
library(usdm)
library(AER)
library(foreign)
library(jsonlite)
library(shiny)
library(ggplot2)
library(knitr)
library(mongolite)
library(scales)
library(DT)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
#Load json file
#m1 <- fromJSON(filename)

#mongoDB connection
#m1 <- mongo(collection = "accounts", 
#            url = "mongodb://abcd:abcd@10.128.0.12,10.128.0.13,10.128.0.14/prayer?replicaSet=ABIDEDB")
#
#d1 <- mongo(collection = "devices", 
#            url = "mongodb://abcd:abcd@10.128.0.12,10.128.0.13,10.128.0.14/prayer?replicaSet=ABIDEDB")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df <- m1$find('{"appleAdAttrib.iad-attribution" : "true"}', 
              field = '{"_id":1,
                        "appleAdAttrib":1,
                        "itunesSubscription.firstSubscribedAt":1,
                        "stripeSubscription.firstSubscribedAt":1
}')
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
dfa <- d1$find('{"appleAdAttrib.iad-attribution" : "true"}', 
              field = '{"appleAdAttrib":1,
                        "accountId":1,
                        "kind":1
}')
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#convert nested df to to a flattened df
df = flatten(df)
dfa = flatten(dfa)
#replace . with _ in column names
names(df) <- gsub("\\.", "_", names(df))
names(df) <- gsub("\\-", "_", names(df))
names(dfa) <- gsub("\\.", "_", names(dfa))
names(dfa) <- gsub("\\-", "_", names(dfa))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#Conversion Column
df$converted <- (!is.na(df$itunesSubscription_firstSubscribedAt) | !is.na(df$stripeSubscription_firstSubscribedAt))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# remove devices from dfa that have an account associated with it
dfa <- dfa[is.na(dfa$accountId),]
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#Format Date Columns
df$appleAdAttrib_iad_purchase_date <- strtrim(df$appleAdAttrib_iad_purchase_date , 10)
df$appleAdAttrib_iad_purchase_date  <- as.Date(df$appleAdAttrib_iad_purchase_date)
df$itunesSubscription_firstSubscribedAt <- strtrim(df$itunesSubscription_firstSubscribedAt, 10)
df$itunesSubscription_firstSubscribedAt <- as.Date(df$itunesSubscription_firstSubscribedAt)
df$stripeSubscription_firstSubscribedAt <- strtrim(df$stripeSubscription_firstSubscribedAt, 10)
df$stripeSubscription_firstSubscribedAt <- as.Date(df$stripeSubscription_firstSubscribedAt)
df$appleAdAttrib_iad_click_date <- strtrim(df$appleAdAttrib_iad_click_date, 10)
df$appleAdAttrib_iad_click_date <- as.Date(df$appleAdAttrib_iad_click_date)

dfa$appleAdAttrib_iad_click_date <- strtrim(dfa$appleAdAttrib_iad_click_date, 10)
dfa$appleAdAttrib_iad_click_date <- as.Date(dfa$appleAdAttrib_iad_click_date)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#add missing columns
dfa$converted <- FALSE
dfa$`_id` <- NA
#drop extra columns
dfa$accountId <- NULL
dfa$kind_platform <- NULL
dfa$kind_version <- NULL
df$itunesSubscription_firstSubscribedAt <- NULL
df$stripeSubscription_firstSubscribedAt <- NULL
df$appleAdAttrib_iad_creative_id <- NULL
df$appleAdAttrib_iad_creative_name <- NULL
#merge data sets
df <- rbind(df, dfa)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#df of selected dates
df1 <- df[df$appleAdAttrib_iad_click_date >= start_date & df$appleAdAttrib_iad_click_date <= end_date,]
dfa <- dfa[dfa$appleAdAttrib_iad_click_date >= start_date & dfa$appleAdAttrib_iad_click_date <= end_date,]
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
num_downloads <- nrow(df1)
search_match <- nrow(df1[which(df1$appleAdAttrib_iad_keyword_matchtype == 'Search Match'),])
broad_match <- nrow(df1[which(df1$appleAdAttrib_iad_keyword_matchtype == 'Broad'),])
redownload <- nrow(df1[which(df1$appleAdAttrib_iad_conversion_type == 'Redownload'),])
download <- nrow(df1[which(df1$appleAdAttrib_iad_conversion_type == 'Download'),])
devices <- nrow(dfa)
accounts <- nrow(df1) - nrow(dfa)
```

#Overview for Reporting Period `r start_date` to `r end_date`

*Number of Downloads with Ad Click:* `r num_downloads`

*Number of Devices without Accounts with Ad Click:* `r devices`

*Number of Accounts with Ad Click:* `r accounts`

*Search Match Hits (keyword unknown):* `r search_match` 

*Broad Match Hits:* `r broad_match`


####Conversion Type as assigned by Apple
*Redownloads:* `r redownload`

*Downloads:* `r download`


#Campaign Conversions

**Description:**  Top performing campaigns based off of the number of downloads.

*Reporting Period:* `r start_date` to `r end_date`

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = "63%"}
table1 <- table(df1$appleAdAttrib_iad_campaign_name, df1$converted)
df_table1 <- as.data.frame.matrix(table1) 
df_table1$campaign <- row.names(df_table1)
df_table1$total <- df_table1$'FALSE' + df_table1$'TRUE'
df_table1 = df_table1[order(df_table1$'TRUE', decreasing = TRUE),]
df_table1 <- top_n(df_table1, num_top_campaigns)
df_table1 <- melt(df_table1, id.var=c('campaign', 'total'))
ggplot(df_table1, aes(x=factor(campaign, levels = rev(unique(campaign))), y=value, fill=variable)) + 
  geom_bar(stat = 'identity') + 
  coord_flip() +
  geom_text(aes(label=ifelse(value > 50, value, "")), position = position_stack(vjust=0.5)) + 
  labs(y = 'Number of downloads', x = 'Campaign Name', fill = 'Subscribed : ') +
  theme(legend.position = "top", axis.text=element_text(size=10), legend.title = element_text(size=14), axis.title = element_text(face='bold'))
```

**Campaign Conversions**
**Description:** Top performing campaigns excluding 'Christian authors & keywords US 25+'

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = "63%"}
df_table2 <- df_table1[!grepl("Christian authors & keywords US 25+", df_table1$campaign),]
ggplot(df_table2, aes(x=factor(campaign, levels = rev(unique(campaign))), y=value, fill=variable)) + 
  geom_bar(stat = 'identity') + 
  coord_flip() +
  geom_text(aes(label=ifelse(value > 0, value, "")), position = position_stack(vjust=0.5)) + 
  labs(y = 'Number of downloads', x = 'Campaign Name', fill = 'Subscribed : ') +
  theme(legend.position = "top", axis.text=element_text(size=10), legend.title = element_text(size=14), axis.title = element_text(face='bold'))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_table_a <- as.data.frame.matrix(table1) 
colnames(df_table_a) <- c('Not Subscribed', 'Subscribed')
df_table_a$'Subscriber %' <- percent(df_table_a$Subscribed/(df_table_a$`Not Subscribed` + df_table_a$Subscribed), accuracy = 0.01)

df_table_a <- df_table_a[order(-df_table_a$Subscribed),]
datatable(df_table_a)

```



# Keyword Conversions

**Description:**  Top performing keywords based off of the number of downloads.

*Reporting Period:* `r start_date` to `r end_date`

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = "63%"}
table1 <- table(df1$appleAdAttrib_iad_keyword, df1$converted)
df_table1 <- as.data.frame.matrix(table1) 
df_table1$keyword <- row.names(df_table1)
df_table1$total <- df_table1$'FALSE' + df_table1$'TRUE'
df_table1 = df_table1[order(df_table1$'TRUE', decreasing = TRUE),]
df_table1 <- top_n(df_table1, num_top_keywords)
df_table1 <- melt(df_table1, id.var=c('keyword', 'total'))
ggplot(df_table1, aes(x=factor(keyword, levels = rev(unique(keyword))), y=value, fill=variable)) + 
  geom_bar(stat = 'identity') + 
  coord_flip() +
  geom_text(aes(label=ifelse(value > 0, value, "")), position = position_stack(vjust=0.5)) + 
  labs(y = 'Number of downloads', x = 'Keyword', fill = 'Subscribed : ') +
  theme(legend.position = "top", axis.text=element_text(size=10), legend.title = element_text(size=14), axis.title = element_text(face='bold'))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_table_a <- as.data.frame.matrix(table1) 
colnames(df_table_a) <- c('Not Subscribed', 'Subscribed')
df_table_a$'Subscriber %' <- percent(df_table_a$Subscribed/(df_table_a$`Not Subscribed` + df_table_a$Subscribed), accuracy = 0.01)

df_table_a <- df_table_a[order(-df_table_a$Subscribed),]
datatable(df_table_a)
```


# Low Conversion Keywords

**Description:**  Keywords with the most downloads that do not have a conversion in the specified time period.

*Reporting Period:* `r start_date` to `r end_date`

```{r echo=FALSE, warning=FALSE, message=FALSE, out.width = "63%"}
df_table1 <- as.data.frame.matrix(table1) 
df_table1$keyword <- row.names(df_table1)
df_table1$total <- df_table1$'FALSE' + df_table1$'TRUE'
df_table1 <- df_table1 %>%
         filter(df_table1$'TRUE'<1)
df_table1 <- df_table1[order(df_table1$'FALSE', decreasing = TRUE),]
df_table1 <- top_n(df_table1, num_top_keywords)
df_table1 <- melt(df_table1, id.var=c('keyword', 'total'))
ggplot(df_table1, aes(x=reorder(keyword, value), y=value, fill=variable)) + 
  geom_bar(stat = 'identity') + 
  coord_flip() +
  geom_text(aes(label=ifelse(value > 0, value, "")), position = position_stack(vjust=0.5)) + 
  labs(y = 'Number of downloads', x = 'Keyword', fill = 'Subscribed : ') +
  theme(legend.position = "top", axis.text=element_text(size=10), legend.title = element_text(size=14), axis.title = element_text(face='bold'))
```

*Includes keywords in the above chart as well as keywords with a less than 5% conversion rate in the given time period*

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_table_a <- as.data.frame.matrix(table1) 
colnames(df_table_a) <- c('Not Subscribed', 'Subscribed')
df_table_a$'Subscriber %' <- (df_table_a$Subscribed/(df_table_a$`Not Subscribed` + df_table_a$Subscribed))
df_table_a <- df_table_a[(df_table_a$`Subscriber %` < 0.05),]
df_table_a$`Subscriber %` <- percent(df_table_a$`Subscriber %`, accuracy =0.01)
df_table_a <- df_table_a[order(-df_table_a$'Not Subscribed'),]
datatable(df_table_a)
```